\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-04-02 popl-2019-journal-v/paper.tex
[POPLjv] Add example to motivate the necessity of sealing

  \caption{Permission hierarchy}
  \label{fig:perm-hier}
\end{wrapfigure}%
%
%%% Seals
% KJAA: Here I am still missing an intuition of what a seal 'is' -- why the range, why the seal as an 'entity'?

@@

In order to seal a sealable with a seal $\sigma$, it is necessary to have the permission to do so.

@@

@@

\subsection{Overlay Semantics}
% Describe the things added to the syntax
The overlay semantics \srccm{} for \trgcm{} views part of the memory as a built-in stack (Figure~\ref{fig:source-syntax}).
% Built-in stack
To this end, it adds a call stack and a free stack memory to the executable configurations of \trgcm{}.
The call stack is a list with all the stack frames that are currently inaccessible because they belong to previous calls.
Every stack frame contains encapsulated stack memory as well as the program point that execution is supposed to return to.
The free stack memory is the active part of the stack that has not been claimed by a call and thus can be used at this point of time.
% Stack pointer
In order to distinguish capabilities for the stack from the capabilities for the rest of the memory, \srccm{} adds stack pointers.
A stack pointer has a permission, range of authority, and current address, just like capabilities on \trgcm{}, but they are always linear.
% Return pointers
The final syntactic constructs added by \srccm{} are the code and data return pointers.
The data return pointer corresponds to some stack pointer (which in turn corresponds to a linear capability), and the code return pointer corresponds to some capability with read-execute permission.
Syntactically, the return capabilities contain just enough information to reconstruct what they correspond to on the underlying machine.
On \srccm{}, return pointers are generated by calls from the capabilities they correspond to on \trgcm{}, and they are turned back to the capabilities they correspond to upon return.
% Even though the return pointers both correspond to capabilities with read permission, neither can be used for reading. 
% Say, we allowed reads through a data return pointer, then that would correspond to reading from some stack memory that is encapsulated in a stack frame which would break LSE.

>>>>

  \caption{Permission hierarchy}
  \label{fig:perm-hier}
\end{wrapfigure}%
%
%%% Seals

@@

In order to seal a sealable with a seal $\sigma$, it is necessary to have the authority to do so.

@@

\begin{jversion}
  \subsection{The purpose of sealing}
  % Sealing example:
  To motivate the necessity of an encapsulation mechanism like sealing, consider the following example.
  We want to transfer control to code that we do not trust, and we want to give them the means to return to us.
  That is, we need to give them a return capability.
  If we did not have an encapsulation mechanism, our only option would be to give them an executable capability for the address we want them to return to.
  The code we give the return capability could use it as intended, but it could also manipulate the return capability to point to a different point and return to an unintended point of our code.
  Further in order to be able to retrieve our capabilities from before transferring control, we would have to store them somewhere accessible from the return capability.
  However, the untrusted code would have access to all this through the return capability because it does not give less authority to the untrusted code than it does to us.
  For this reason, any reasonable capability machine must have an encapsulation mechanism to enable programs to make boundaries between security domains.

  In the example, if we use sealing, we can seal the return capability which does two things.
  It prevents the untrusted code from changing the target of the return capability forcing them to return to the point we intended.
  It also prevents the untrusted code from reading our capabilities.
  All in all, this means that we can transfer control to another domain without giving up our capabilities or handing them over.
\end{jversion}

@@

\subsection{Overlay Semantics}
\label{subsec:overlay-semantics}
% Describe the things added to the syntax
The overlay semantics \srccm{} for \trgcm{} views part of the memory as a built-in stack (Figure~\ref{fig:source-syntax}).
% Built-in stack
To this end, it adds a call stack and a free stack memory to the executable configurations of \trgcm{}.
The call stack is a list with all the stack frames that are currently inaccessible because they belong to previous calls.
Every stack frame contains encapsulated stack memory as well as the program point that execution is supposed to return to.
The free stack memory is the active part of the stack that has not been claimed by a call and thus can be used at this point of time.
% Stack pointer
In order to distinguish capabilities for the stack from the capabilities for the rest of the memory, \srccm{} adds stack pointers.
A stack pointer has a permission, range of authority, and current address, just like capabilities on \trgcm{}, but they are always linear.
% Return pointers
The final syntactic constructs added by \srccm{} are the code and data return pointers.
The data return pointer corresponds to some stack pointer (which in turn corresponds to a linear capability), and the code return pointer corresponds to some capability with read-execute permission.
Syntactically, the return capabilities contain just enough information to reconstruct what they correspond to on the underlying machine.
On \srccm{}, return pointers are generated by calls from the capabilities they correspond to on \trgcm{}, and they are turned back to the capabilities they correspond to upon return.
% Even though the return pointers both correspond to capabilities with read permission, neither can be used for reading. 
% Say, we allowed reads through a data return pointer, then that would correspond to reading from some stack memory that is encapsulated in a stack frame which would break LSE.
